---
layout: page
title: Publications
permalink: /pub/
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
library(methods)
library(scholar)
bob <- get_profile("2CiKnzkAAAAJ")
paste("{\\small H-Index ", bob$h_index, " (", bob$total_cites, " citations as of ", date(), ")}",sep="")
bob<-get_publications("2CiKnzkAAAAJ")
write.table(file="./tempcites.txt", data.frame(bob$cid,bob$cites), row.names=F, quote=F, col.names=F)
```

```{r, eval=FALSE, echo=FALSE}
source("data/googleCite.r")
out = googleCite("https://scholar.google.com/citations?hl=en&user=2CiKnzkAAAAJ",pdfname="figure/wordcloud.pdf")
```

```{r, eval=FALSE, echo=FALSE}
library(RefManageR)
b <- ReadBib("data/citations_2016.bib", check=FALSE)

b2 <- ReadGS(scholar.id="2CiKnzkAAAAJ", check.entries = FALSE)
print(b2, .opts= list(bib.style = "authoryear"))
```

Koesterke, L, D. Stanzione, M. Vaughn, et al. (2011). “An efficient and
scalable implementation of SNP-pair interaction testing for genetic
association studies”. In: _Parallel and Distributed Processing
Workshops and Phd Forum (IPDPSW)_ 2011.

Leiboff, S, X. Li, H. C. Hu, et al. (2015). “Genetic control of
morphometric diversity in the maize shoot apical meristem”. In: _Nature
communications_ 6.

Liu, S, K. Ying, C. T. Yeh, et al. (2012). “Changes in genome content
generated via segregation of non‐allelic homologs”. In: _The Plant
Journal_ 72.3, pp. 390-399.

Sosso, D., D. Luo, Q. B. Li, et al. (2015). _Seed filling in
domesticated maize and rice depends on SWEET-mediated hexose
transport_. Tech. rep. Nature genetics.

Yang, J, H. Jiang, C. T. Yeh, et al. (2015). “Extreme‐phenotype
genome‐wide association study (XP‐GWAS): a method for identifying
trait‐associated variants by sequencing pools of individuals selected
from a diversity panel”. In: _The Plant Journal_ 84.3, pp. 587-596.



This is the base Jekyll theme. You can find out more info about customizing your Jekyll theme, as well as basic Jekyll usage documentation at [jekyllrb.com](http://jekyllrb.com/)

You can find the source code for the Jekyll new theme at: [github.com/jglovier/jekyll-new](https://github.com/jglovier/jekyll-new)

You can find the source code for Jekyll at [github.com/jekyll/jekyll](https://github.com/jekyll/jekyll)


